\section[Conclusion]{Conclusion \& Future Work}

\begin{frame}{Summary of Part I}
    \begin{block}{CMP \& Surrogate Acceleration}
        \begin{itemize}
            \item \textbf{Bridging the Gap:} CMP unifies Full Bayesian exactness with Modular calibration speed.
            \item \textbf{No False Certitude:} Decouples hyperparameter optimization while preserving Full Bayesian bounds.
            \item \textbf{Acceleration (AS-hGP):} Expected Variance Reduction drastically speeds up inference.
            \item \textbf{Validation:} Successfully resolved missing data and severe model error in hypersonic flows.
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Summary of Part II}
    \begin{block}{Piecewise Emulation of Discontinuous Responses}
        \begin{itemize}
            \item \textbf{Data-Driven Discovery:} Emulates discontinuous physics without prior expert knowledge.
            \item \textbf{Iterative Coupling:} Unifies clustering, classification, and regression into a robust loop.
            \item \textbf{Overcoming Limitations:} Successfully eliminates Gibbs oscillations and global regressor smearing.
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Future Perspectives}
    \begin{itemize}
        \item \textbf{Active Learning for Piecewise Surrogates:} Extend the Expected Variance Reduction criterion (ALC) to efficiently train the clustering-based surrogate model (non-Gaussian mixture).
        \item \textbf{Integration:} Directly couple the piecewise emulator within the calibration loop to enable robust inference for discontinuous physics (e.g., icing regime shifts).
    \end{itemize}
    \vspace{0.5cm}
    \begin{center}
        \begin{tikzpicture}
            \node[draw, rounded corners, fill=green!10, text width=4cm, align=center] (uq) {Robust UQ \& Calibration};
            \node[draw, rounded corners, fill=orange!10, text width=4cm, align=center, right=1.5cm of uq] (surr) {Piecewise Emulation};
            
            \draw[<->, thick, shorten >=2pt, shorten <=2pt] (uq) -- (surr);
            \node[below=0.2cm of uq, text width=4cm, align=center, font=\small] {Identifies domains of interest};
            \node[below=0.2cm of surr, text width=4cm, align=center, font=\small] {Accelerates inference};
        \end{tikzpicture}
    \end{center}
\end{frame}

\begin{frame}{Impact on the Future of In-Flight Icing Research}
    \begin{itemize}
        \item Enable truly probabilistic morphogenetic models.
        \item Combine UQ techniques with similarity measures of ice shapes.
        \item Design robust anti-icing systems through global sensitivity and the Icing Severity Index (ISI).
    \end{itemize}
    \vspace{0.5cm}
    \begin{block}{Final Remark}
        The methodological advancements of this thesis provide the mathematical foundation required to transition highly complex aerospace phenomena towards a reliable, simulation-based design and virtual certification paradigm.
    \end{block}
\end{frame}
