% !TEX root = ../my-thesis.tex
%
\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\addchap*{Acknowledgement}
\label{sec:acknowledgement}

I would like to express my sincere gratitude to my supervisors, Pietro, Enora, and Giulio, for their guidance and support throughout this journey. When I started my PhD, I naively thought that the goodness of a PhD supervisor can be measured by their number of papers, their number of citations, or their h-index. Oh boy, I couldn't have been more wrong! I consider myself very lucky to have had the opportunity to have been supervised by excellent supervisors, who not only are all \textbf{brilliant} scientists but also \textbf{wonderful} human beings. Thank you Pietro, Enora and Giulio for guiding me in the right direction, for giving me the freedom to explore what I felt was interesting, for helping me to feel confident in my work, and for \textbf{always} being there, no matter what, when I needed help, advice, or just a chat. Thank you for having understood me as a researcher and as a person, thank you for pushing more on the accelerator when I was accelerating and for pressing the brake when I needed it. Thank you also to my \textit{informal} supervisor, Olivier Le Maitre, for your support. Your passion for what you do, and your rigour have been contagious and inspiring. I was lucky to have you as a supervisor, and I am grateful for all the time and effort you have dedicated to me.

\smallskip
Thank you to all the TRACES network, thank you Alberto for believing in me and for giving me the opportunity to be part of this amazing network, and thank you to all the TRACES doctoral students for all the fun (and beers) we had together. You are all brilliant researchers and wonderful people, and I am grateful to have had the opportunity to meet you and work with you. 
\smallskip
Thank you to my fellow RandoCité organizers for believing in this project and for giving me the opportunity to help people connect, hike and have fun together. I am so happy to hear that RandoCité is still going strong, and I am grateful to have been able to slightly improve the lives of some people in this way. Thank you to all the people I've met at CITEU, thank you for making me feel at home and for all the fun we had together.

\smallskip
Merci a tous mes amis et collègues du Platon, pour les moments de joie et de détente que nous avons partagés ensemble. Je suis reconnaissant d'avoir eu l'opportunité de travailler avec vous et de faire partie de cette communauté. Vous êtes tous des personnes formidables et des chercheurs brillants, je suis fier de pouvoir vous appeler mes amis et je vous souhaite à tous le meilleur pour l'avenir. Travailler avec vous, partager des idées et des expériences, parler de science et de vie pendant les pauses café, et rire ensemble, a été une expérience inoubliable. Merci pour votre soutien et votre amitié, et j'espère que nous resterons en contact pour les années à venir.

\smallskip
Grazie anche ai miei amici expat italiani a Parigi, Lorenzo, Gianmarco e Vittorio, per avermi fatto sentire un po' meno lontano da casa e per tutti i momenti di divertimento che abbiamo condiviso insieme. Voi 4 siete stati il mio punto di riferimento per tutto a Parigi, dalle giornate spese per ricevere la Carte Vitale, alle nottate passate a discutere di come fare la dichiarazione dei redditi, fino alle serate passate in giro per Parigi. 

\smallskip
Grazie ai miei amici di infanzia e adolescenza, per essere ancora presenti nella mia vita e per il supporto che mi avete sempre dato, anche a distanza. 

\smallskip
Grazie alla mia famiglia, per essere sempre stata al mio fianco, e per avermi sempre spinto a dare il massimo in tutto quello che faccio. Voglio ringraziare in particolare mio Papà, per essere l'unico uomo che sogna con tutto se stesso di vedermi volare più in alto di lui. Mamma, anche durante la tua malattia mi hai sempre dato la forza di andare avanti e di non mollare mai. \textbf{Per questo voglio dedicare a te questa tesi, perchè se oggi sono qui è anche grazie a te, alla tua forza, al tuo coraggio e alla tua determinazione}. Voglio ringraziare anche mio nonno Armando, che oggi mi guarda dall'alto del paradiso, per essere sempre stato un esempio e modello di vita per me. Ivan, Giulio, Frank, Marcello, Cristina, Anselmo, Tonino, Giovanna, Alessandro, Paolo, Giuliana, Riccardo e Maria, e tutti gli altri membri della mia famiglia, grazie per essere sempre stati presenti nella mia vita e per il supporto che mi avete sempre dato.


\smallskip
Pahápe, muchas gracias a mi enfermera \textit{chiquitita}, Diana, por ser mi compañera de vida, por apoyarme en todo momento, y por hacerme sentir amado y cuidado. Cuando te conocí, no sabía que podía ser tan feliz, y ahora no puedo imaginar mi vida sin ti. Gracias por tu paciencia, por tu amor, siempre mas grande que el numero de Graham + 1. Te amo con todo mi corazón, y te estaré siempre agradecido por ser parte de mi vida. No puedo esperar a seguir construyendo nuestra vida juntos, y a seguir creciendo como personas y como pareja. Gracias por ser mi compañera de vida, mi amiga, mi confidente, y mi amor. Te amo con todo mi corazón, y siempre te amaré.
\textbf{Rohayhu, che mborayhu.}
